Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-03-31 paper/main.tex

Recall that each of $A_{1}, \ldots, A_{B_1}$ were selected from groups of independent projections of size $B_2$.  Let $P_{b_1} := A_{b_1}^TA_{b_1}$, for $b_1, \ldots, B_n$, which can be seen as the $p$-dimensional version of $A_{b_1}$. Then define
\[
\bar{\Pi} := \frac{1}{B_1} \sum_{b_1 = 1}^{B_1} \Pi_{b_1} =  \frac{1}{B_1} \sum_{b_1=1}^{B_1} A_{b_1}^TA_{b_1}.
\]

@@

We present two simulation studies, of distributions with known central subspaces, and compare our method with other techniques for supervised dimension reduction. \\
~\\
\textbf{Sparse class boundaries}\\
First, we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma). \]
We set $p=100$, $\mu_0 = (2, -2, 0, \ldots, 0)^T$, $\mu_1 = (2, 2, 0, \ldots, 0)^T$ and let $\Sigma = I_{100}$. This model exhibits a setup in which a central subspace exists (of dimension $d^* = 2)$, but there is no good linear class boundary. \\
~\\

\begin{table}
  \caption{Simulation performance}
  \label{sample-table}
  \centering
  \begin{tabular}{l|lll|lll}
    \toprule
    \multicolumn{2}{c}{Model 1} & \multicolumn{2}{c}{Model 2}                     \\
    \cmidrule(r){1-4}
    Method     & Power     & False & Accuracy &  Power     & False & Accuracy &  \\
    & & Discovery & & & Discovery &
    \midrule
    RP-LDA & Input terminal  & $\sim$100  &  &&& \\
    RP-QDA    & Output terminal & $\sim$10    &  &&&\\
    RP-kNN     & Cell body       & up to $10^6$ & &&& \\
    \bottomrule
  \end{tabular}
\end{table}

@@

where $\Sigma_p$ is a random $p\times p$ rotation. We choose $\mu_0 = (3, 3, 3, 0, \ldots, 0)$ and $\mu_1 = (0, \ldots, 0)$, while $\Sigma0$ and $\Sigma_1$ are block diagonal

>>>>

Recall that each of $A_{1}, \ldots, A_{B_1}$ were selected from groups of independent projections of size $B_2$.  Let $P_{b_1} := A_{b_1}^TA_{b_1}$, for $b_1, \ldots, B_n$, which can be seen as the $p$-dimensional version of $A_{b_1}$. Then define
\[
\bar{\Pi} := \frac{1}{B_1} \sum_{b_1 = 1}^{B_1} \Pi_{b_1} =  \frac{1}{B_1} \sum_{b_1=1}^{B_1} A_{b_1}^TA_{b_1}.
\]
\tcnote{Compare with: 
\[
\Bigl(\bar{\Pi} -\mathbb{E}(A^TA) \Bigr)^2 =  \Bigl(\bar{\Pi} - \frac{d}{p} I_{p\times p}\Bigr)^2
\]
This gave us the same answer, right?}

@@

\jbnote{Power $\rightarrow$ power rate, accuracy $\rightarrow$ accuracy + bayes risk}
We present two simulation studies, of distributions with known central subspaces, and compare our method with other techniques for supervised dimension reduction. \\
~\\
\textbf{Sparse class boundaries}\\
First, we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma). \]
We set $p=100$, $\mu_0 = (2, -2, 0, \ldots, 0)^T$, $\mu_1 = (2, 2, 0, \ldots, 0)^T$ and let $\Sigma = I_{100}$. This model exhibits a setup in which a central subspace exists (of dimension $d^* = 2)$, but there is no good linear class boundary. \\
~\\

\begin{table}
  \caption{Simulation performance}
  \label{sample-table}
  \centering
  \begin{tabular}{l|lll|lll}
    \toprule
    & \multicolumn{3}{c}{Model 1} & \multicolumn{3}{c}{Model 2}                     \\
    \cmidrule(r){1-7}
    Method     & Power     & FD & Accuracy &  Power     & FD & Accuracy   \\

    \midrule
    RP-LDA & 0.185 & 1.82  &  0.553 & 0.897 & 1.10 & 0.945 \\
    RP-QDA & 1.65  & 0.350 & 0.899 & 0.902 & 1.10 & 0.945 \\
    RP-kNN & 1.58  & 0.417 & 0.908 & 0.938 & 1.06 & 0.945 \\
    SIR & 0.417 & 1.58 & 0.539 & 0.677 & 1.32 & 0.945 \\
    SAVE & 1.42 & 0.575 & 0.882 & 1.07 & 0.931 & 0.931 \\
    PHD & 1.23 & 0.765 & 0.867 & 0.0352 & 1.96 & 0.465 \\
    PCA & 1.94 & 0.0593 & 0.93 & 0.997 & 1.00 & 0.940 \\
    Lt-SNE & 0.0137 & 1.986 & 0.477 & 0.0589 & 1.94 & 0.581 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

where $\Sigma_p$ is a random $p\times p$ rotation. We choose $\mu_0 = (3, 3, 3, 0, \ldots, 0)$ and $\mu_1 = (0, \ldots, 0)$, while $\Sigma_0$ and $\Sigma_1$ are block diagonal
